\thesistitle

### 2019-08-24 sections/discussion.tex
Discussion

\chapter{Discussion}
\label{ch:discussion}
%Interpretations: what do the results mean?
%Implications: why do the results matter?
%Limitations: what can’t the results tell us?
%Recommendations: what practical actions or scientific studies should follow?

@@

\section{Clone Type Definitions}
In this study, we proposed a set of clone type definitions that can be automatically refactored.  We based these clone type definitions on the clone type definitions that are commonly used in literature. The design of these clone type definitions entails some decisions that have a large impact on the clones we considered for refactoring in this study. In this section we discuss our clone type definitions as proposed in Section~\ref{sec:rtypes}.

@@

\section{Clone Context Analysis}
In Section~\ref{chap:contextsetup} we introduced the categories we defined for mapping the context of clones. In this section, we discuss this together with the related experiments.

@@

\subsection{Context Analysis}
In this study we identified categories for three properties of clones: relation, location and contents. %Mapping the location and contents was mainly to find out what the best method of refactoring is to refactor most clones.
We chose a set of relations that indicate different refactoring opportunities. However, as our CloneRefactor tool only analyses Java source code, we we biased towards categories that are often found in Java source code. For other languages, other categories might be valuable to analyze to find suitable categories for that programming language.

@@

\subsection{Clone Types}
In this section, we discuss the differences between clone types 1-3 and 1R-3R. We see that the difference between T1R and T1 in terms of found clones is small (11\%). This implies that most often textually equal code is also functionally equal. The difference between T2R and T2 is bigger (35\%). Upon manual inspection we found that the main reason for this is that T2R does not allow any variability in types, wheareas T2 allows any variability in types.

Regarding performance (Figure~\ref{fig:performance}, there is a notable difference between the refactoring-oriented clone types and the literature clone types. Type 1R-3R take about 6 times longer to detect than type 1-3. The main reason for this is type resolution: finding the fully qualified identifiers of type-, variable- and method-references.

@@

In Figure~\ref{fig:t3rgraph} we show the increase of cloned nodes for higher type 3R gap sizes. The line denoting the number of clone classes seems a bit exponential whereas the line denoting cloned nodes is mostly linear. This makes sense regarding the nature of the threshold. As we get into higher gap size percentages, fewer clones merge (thus the decrease in amount of clone classes merging). However, at these higher gap size percentages the gaps contains more nodes (thus the amount of cloned nodes being linear).

@@

\subsection{Extract Method}
28\% of clones can be refactored using the ``Extract Method'' refactoring technique (50\% if we limit our searching scope to method bodies). About 25\% of clones do not span part of a method, because of which they cannot be refactored. Many clones (23\%) do not have a statement as top-level AST-Node. Upon manual inspection, we noticed that the main reason for this is clones in anonymous functions or anonymous classes. About 15\% of clones span only part of an AST-Node.

\subsection{Refactoring}
In Fig.~\ref{fig:maintainabilityscore} we see an increase in maintainability for refactoring larger clone classes. The tipping point, between a better maintainable refactoring and a worse maintainable refactoring, seems to lie at a token volume of 63 tokens. There are fewer large clones than small clones, resulting in a very limited statistical significance on our corpus when considering clones larger than 100 tokens.

In Table~\ref{tab:relationref} we see the results regarding refactorings that are applied to clones with diverse relations. We see that most refactored clones are in a common class, over 54\%. This is significantly more than the percentage of clones in the common class relation as reported in Table~\ref{tab:relation}. Meanwhile, the number of refactored unrelated clones is smaller than the number reported in Table~\ref{tab:relation} (24\% -> 18\%). The main reason for this is that refactoring unrelated clones can change the relation of other clones in the same system. If we create a superclass abstraction to refactor an unrelated clone, other clones in those classes that were previously unrelated might become related.

The maintainability scores displayed in Table~\ref{tab:relationref} show that the most favorable clones to refactor are clones with a sibling relation. The most unfavorable is to refactor clones to interfaces. However, the differences in maintainability in this table are generally small; according to our data relations have a minor impact on the maintainability of clones.

Regarding the return type of refactored clones, we see in Table~\ref{tab:return} that this has no major impact on maintainability. A method call to the extracted method that is directly returned and no return type extracted methods are slightly more favorable than the others. We think the main reason that the ``Return'' category is on top is that when a variable is declared at the end of the cloned fragment, CloneRefactor directly returns its value and removes the declaration. This decreases the volume slightly.

A higher number of parameters directly influences the corresponding metric. Because of this, we see in Fig.~\ref{fig:arguments} that more parameters negatively influence maintainability. Not only the number of parameters metric is negatively influenced, but more method parameters also increase volume for the extracted method and each of the calls to it. Because of that, we see that trend of the graph in Fig.~\ref{fig:arguments} decreases relatively rapidly.

>>>>

\chapter{Discussion} \label{ch:discussion}

@@

\section{Clone Type Definitions}
In this study, we proposed a set of clone type definitions that can be automatically refactored. We based these clone type definitions on the clone type definitions that are commonly used in literature \cite{roy2007survey}. The design of these clone type definitions entails some decisions that have a large impact on the clones we considered for refactoring in this study. In this section we discuss our clone type definitions as proposed in Section~\ref{sec:rtypes}.

@@

%\section{Clone Context Analysis}
%In Section~\ref{chap:contextsetup} we defined categories for mapping the context of clones. In this section, we discuss this together with the related experiments.

@@

\subsection{Context Analysis}
In this study we identified categories for three properties of clones: relation, location and contents. We chose a set of relations that indicate different refactoring opportunities. However, as our CloneRefactor tool only analyses Java source code, we we biased towards categories that are often found in Java source code. For other languages, other categories might be valuable to analyze to find suitable categories for that programming language.

@@

\subsection{Clone Types}
In this section, we discuss the differences between clone types 1-3 and 1R-3R. We see that the difference between T1R and T1 in terms of found clones is small (11\% more nodes found as cloned for T1). This implies that most often textually equal code is also functionally equal. The difference between T2R and T2 is bigger (35\% more nodes found as cloned). Upon manual inspection, we found that the main reason for this is that T2R does not allow any variability in types, wheareas T2 allows any variability in types.

Regarding performance (Figure~\ref{fig:performance}, there is a notable difference between the refactoring-oriented clone types and the literature clone types. Type 1R-3R take on average approximately 6 times longer to detect than type 1-3. The main reason for this is type resolution: finding the fully qualified identifiers of type-, variable-, and method-references.

@@

In Figure~\ref{fig:t3rgraph} we show the increase of cloned nodes for higher type 3R gap sizes. The line denoting the number of clone classes seems a bit exponential whereas the line denoting cloned nodes is mostly linear. This makes sense regarding the nature of the threshold. Type 3R clones are formed by merging two gapped clone classes into a type 3R clone class. As we get into higher gap size percentages, fewer clone classes merge. However, at these higher gap size percentages the gaps contains more nodes , because of which the increase of the number of cloned nodes is linear.

@@

\subsection{Extract Method}
28\% of clones can be refactored using the ``Extract Method'' refactoring technique. About 25\% of clones do not span part of a method, because of which they cannot be refactored. 23\% of the clones do not have a statement as top-level AST-Node. Upon manual inspection, we noticed that the main reason for this is when clones reside in anonymous functions or anonymous classes. About 15\% of clones span only part of an AST-Node.

\subsection{Refactoring}

\subsubsection{Token Volume}
In Fig.~\ref{fig:maintainabilityscore} we see an increase in the \textbf{maintainability score} for refactoring larger clone classes. The tipping point, between a better maintainable refactoring and a worse maintainable refactoring, lies at a token volume of 63 tokens. There are fewer large clones than small clones (exponential decrease), resulting in a very limited statistical significance on our corpus when considering clones larger than 100 tokens.

When looking at the relation between maintainability and the \textbf{volume} metric, we see that the volume increases if the average clone volume is less than 60 tokens, but decreases above 60 tokens. When token volume increases, the \textbf{number of parameters} of the extracted method rises very slowly. Overall, on average, extracted methods have only one parameter. When the token volume of clones becomes larger than 160 tokens, we also see that there are more outliers in terms of number of parameters. For the \textbf{complexity} we see that most clones do not have any complexity, because for most refactorings the complexity increases by one. This complexity is the added complexity of the extracted method, and implies that the removed clones did not have any complexity. There is also no clear trend regarding the complexity.

\subsubsection{Relation}
In Table~\ref{tab:relationref} we see the results regarding refactorings that are applied to clones with the specified relation category. We see that 57\% of the refactored clones are in a common class. This is significantly more than the percentage of clones in the common class relation as reported in Table~\ref{tab:relation}. Meanwhile, the number of refactored unrelated clones is smaller than the number reported in Table~\ref{tab:relation} (24\% -> 17\%). The main reason for this is that refactoring unrelated clones can change the relation of other clones in the same system. If we create a superclass abstraction to refactor an unrelated clone, other clones in those classes that were previously unrelated become related.

The maintainability scores displayed in Table~\ref{tab:relationref} show that the most favorable clones to refactor are clones with a superclass relation. The most unfavorable is to refactor unrelated clones. The main reason for this difference in maintainability is that on average unrelated clones have a higher volume.

The differences in maintainability of relation are, compared to the differences in maintainability of different token volumes, very small. Common hierarchy (which has the highest score) has a maintainability score of 0.23 whereas unrelated clones (which has the lowest score) have a maintainability score of -0.15. This is a very small difference, which implies that according to our data relations have a minor impact on the maintainability of clones.

\subsubsection{Return Category}
Regarding the return category of refactored clones, we see in Table~\ref{tab:return} that this has no major impact on maintainability: the differences between the maintainability scores of the categories are very small. The worst maintainable return category is when methods do not return anything (void), mainly because it is related with a higher number of parameters in the extracted method.

\subsubsection{Number of Parameters}
We see in Figure~\ref{fig:arguments} that the average extracted method that requires more than one parameter decreases maintainability. This is because a higher number of parameters does not only increase the ``number of parameters'' metric, but also the volume for the extracted method and each of the calls to it. Because of that, we see that trend of the graph in Fig.~\ref{fig:arguments} decreases relatively rapidly and that the number of parameters in the extracted method has a major influence on maintainability.

### 2019-08-24 sections/results.tex
Discussion

\chapter{Results}\label{ch:results}
In this chapter, we present the results of our experiments. We perform exploratory experiments to map the differences between clone types, contexts and refactoring opportunities.

@@

\subsection{Clone Token Volume}
Figure \ref{fig:maintainabilityscore} shows the obtained results when plotting the clone volume vs the maintainability increase/decrease. We define the \textit{token volume} as the combined number of tokens in all clone instances in a refactored clone class. The maintainability score, as shown in Figure \ref{fig:maintainabilityscore}, is the average delta maintainability score of all clone classes with the specified token volume that are refactored. For higher token volume numbers we have less refactorings that refactor such clones, because of which we represent the x-axis as a logaritmic scale. The trendline intersects the ``zero'' line (maintainability does not increase nor decrease) at a token volume of 63.

@@

\begin{table}[H]
\centering
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}lrrrrrr@{}}
\toprule
\textit{\textbf{Return Category}} & \textit{\textbf{Complexity}} & \textit{\textbf{Parameters}} & \textit{\textbf{Size}} & \textit{\textbf{Duplication}} & \textit{\textbf{\#}} & \textit{\textbf{Score}} \\ \midrule
Return & 0.85 & 1.02 & -3.84 & -55.00 & 1,571 & 0.19 \\
Declare & 0.94 & 0.74 & 11.11 & -49.19 & 5,177 & 0.15 \\
\rowcolor[HTML]{FFCCC9}
Assign & 0.79 & 1.07 & 0.43 & -56.29 & 14 & 0.12 \\
Void & 0.76 & 1.49 & -5.85 & -56.35 & 5,921 & -0.18 \\ \midrule
\textbf{Grand Total} & \textbf{0.84} & \textbf{1.12} & \textbf{1.33} & \textbf{-53.26} & \textbf{12,683} & \textbf{0.00} \\ \bottomrule
\end{tabular}%
}
\caption{Average metric values for refactorings of clone classes with the specified return category}
\label{tab:return}
\end{table}

>>>>

\chapter{Results}\label{ch:results}
In this chapter, we present the results of our experiments\footnote{The underlying datasheets for all our results can be found on GitHub: \url{https://github.com/SimonBaars/Master-Thesis-Simon-Baars/tree/master/results}}. We perform exploratory experiments to map the differences between clone types, contexts and refactoring opportunities.

@@

\subsection{Clone Token Volume}
Figure \ref{fig:maintainabilityscore} shows the obtained results when plotting the clone volume against the maintainability increase/decrease. We define the \textit{token volume} as the combined number of tokens in all clone instances in a refactored clone class. The maintainability score, as shown in Figure \ref{fig:maintainabilityscore}, is the average delta maintainability score of all clone classes with the specified token volume that are refactored. For higher token volume numbers we have less refactorings that refactor such clones, because of which we represent the x-axis as a logaritmic scale. The trendline intersects the ``zero'' line (maintainability does not increase nor decrease) at a token volume of 63.

@@

\begin{table}[H]
\centering
%\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}lrrrrrr@{}}
\toprule
\textit{\textbf{Return Category}} & \textit{\textbf{Complexity}} & \textit{\textbf{Parameters}} & \textit{\textbf{Size}} & \textit{\textbf{Duplication}} & \textit{\textbf{\#}} & \textit{\textbf{Score}} \\ \midrule
Return & 0.85 & 1.02 & -3.84 & -55.00 & 1,571 & 0.19 \\
Declare & 0.94 & 0.74 & 11.11 & -49.19 & 5,177 & 0.15 \\
\rowcolor[HTML]{FFCCC9}
Assign & 0.79 & 1.07 & 0.43 & -56.29 & 14 & 0.12 \\
Void & 0.76 & 1.49 & -5.85 & -56.35 & 5,921 & -0.18 \\ \midrule
\textbf{Grand Total} & \textbf{0.84} & \textbf{1.12} & \textbf{1.33} & \textbf{-53.26} & \textbf{12,683} & \textbf{0.00} \\ \bottomrule
\end{tabular}%
%}
\caption{Average metric values for refactorings of clone classes with the specified return category}
\label{tab:return}
\end{table}
